%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Freelance Consultant : Integration Technical Lead at Nethys (VOO)} % Job title
    {Jisko (Owner)} % Organization
    {Charleroi, Belgium} % Location
    {Dec. 2019 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Take the ownership of multiple technical components, for their development, their maintenance \& operational support}
        \item {Leading the existing team through different technical improvements of the current architecture}
        \item {Coaching the existing team for their current development Stack}
      \end{cvitems}
  }

  \cventry
    {Consultant : Elastic Stack Expert at Eloy} % Job title
    {Oniryx} % Organization
    {Liège, Belgium} % Location
    {Jan. 2019 - Mar. 2019} % Date(s)
    {
      Setup of an Elastic Stack environment for a custom search engine to allow the customer to find all the records related to a search in all their different systems.
    }

\cventry
  {Consultant : Java Integration Developer \& Technical Evolutions Architect at Le Forem} % Job title
  {Oniryx} % Organization
  {Charleroi, Belgium} % Location
  {Jan. 2017 - Dec. 2019} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Performed technical integration (Security, Resiliency, Logging, Monitoring) between back-ends.}
      \item {Back-end development of technical orchestrations taking into account clustering, resilience, technological constraints, functional constraints (timing, etc \dots).}
      \item {Various POC carried out in a continuous improvement effort: Continuous Delivery with Jenkins, presentation of different Git workflows like Gitflow, optimization of the Camel integration framework usage.}
      \item {Participate in technical architecture meetings of the above-mentioned development.}
    \end{cvitems}
  }

  \cventry
    {Consultant : Java Integration Developer, Operational Support at Nethys (VOO)} % Job title
    {Adneom Benelux} % Organization
    {Brussels \& Liège, Belgium} % Location
    {Nov. 2014 - Jan. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {End-to-end development of integration flows between various back-ends.}
        \item {Development of technical orchestration for regular Batch flows.}
        \item {UML documentation of realized flows (Sequences, Mapping) and in Enterprise Integration Patterns.}
        \item {End-to-end management of the development phase of the flows and modules developed, including: Analysis, Unit Testing, Reviewing, Releasing, Deployment, Monitoring.}
        \item {Follow-up of production deployment, bugs / fixes related to production, and support for workarounds separating the two. Follow-up of production incidents, for example of infrastructure, and management of guards.}
        \item {Scripting of tools automating certain stages of development, such as for release management.}
      \end{cvitems}
    }


\end{cventries}
