%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Summary}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cvparagraph}

%---------------------------------------------------------
Hi, I'm Jonathan. I'm a Software Engineer specialized in Java back-end development for integration environments. 
However, my developer's life doesn't end there since I'm a passionate IT guy who also write lot of Python code and is always thrilled to learn new stuff.
"Stuff" is a various amount of things : New Languages, Frameworks, Methodologies, Architectures\dots and even a bit on the infrastructure side. 
I also really like Open Source since I strongly believe that open contribution is a major driver of continuous improvement of Softwares.
I tend to wander on different community site, making my little contributions on some of my most used libraries, or help others on site like stackoverflow.com.

I'm methodic when it comes to solving problems, since I think method is what allows us to find solutions to problems we haven't met yet. 
I also put a lot of emphasis on understanding how underlying things work, since this knowledge is often useful in many more than one context. 
For example, I love to learn how Networks or Operating Systems work to better understand how my code will behave in certain conditions.

I also really like teaching people, doing talks and coaching people. I believe than when you share knowledge, you also improve your own understanding 
of the things you teach, and the questions you get can show you things you haven't thought about yet : it's a win-win solution in which both parties grow.

\end{cvparagraph}
