%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Publications \& Talks}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
{Owner}
{The Belgian Coder}
{Youtube}
{2021}
{
  \begin{cvitems}
    \item Youtube channel recently created to talk about technology, software engineering and everything related.
    \item Link : \url{https://www.youtube.com/channel/UCHMhsDNqGGE9lxLWARxNUJw}
  \end{cvitems}
}

\cventry
{Speaker} % Role
{Talk : Azure Functions: Guide to Zero Waste in the Cloud } % Title
{Global Azure Belgium} % Location
{2020} % Date(s)
{
  \begin{cvitems}
    \item Live demo of Azure Functions and the challenges that Serverless architectures arises
    \item Link : \url{https://www.youtube.com/watch?v=kuYU_PVt0c8&t=23176s}
  \end{cvitems}
}

\cventry
{Speaker} % Role
{Talk : Docker Swarm Locally, craziness or unsuspected tool? } % Title
{DevDay Belgium} % Location
{2018} % Date(s)
{
  \begin{cvitems}
    \item Live demo of Docker Swarm and how it can be useful to use it locally even if the client doesn't. 
    \item Link : \url{https://www.youtube.com/watch?v=JeBzVX0wjC4}
  \end{cvitems}
}

\cventry
{Author} % Role
{KinectBalls: An Interactive Tool for Ball Throwing Games} % Title
{Springer International Publishing} % Location
{2013} % Date(s)
{
  \begin{cvitems} % Description(s)
    \item {We present a tool that was developed in the context of the first author’s masters project. The tool implements an interactive computer game combining the real and the virtual world in a seamless way. The player interacts with the game by throwing balls towards a wall on which a virtual 3D scene is projected. Using the Kinect 3D sensor, we compute and predict the trajectory, speed and position of the ball. Upon impact with the screen, a virtual ball continues its trajectory in the virtual scene, and interacts with the objects around it using a physical and a graphical 3D engine Bullet, and Ogre3D. The prototype game has been successfully tested on a large number of people of varying ages.}
    \item Live demo during the Spring of Sciences 2013 : \url{https://www.youtube.com/watch?v=v02BcA-EPrI&t=1s}
  \end{cvitems}
}
\cventry
{Talker} % Role
{KinectBalls: An Interactive Tool for Ball Throwing Games} % Event
{INTETAIN 2013} % Location
{Jul. 2013} % Date(s)
{
  \begin{cvitems} % Description(s)
    \item {Presentation of my related publication during the 5th International Conference on Intelligent Technologies for Interactive Entertainment (INTETAIN).}
  \end{cvitems}
}



%---------------------------------------------------------
\end{cventries}
